---
title: "HW2"
author: "Ian Mulchrone"
date: "2026-01-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 4a

$P(x<2) = 1 - e^{-(1/10)*2}$ <br>
$P(x<2) = 1 - e^{-0.2}$ <br>
$P(x<2) = 0.181269$ <br>
$1000*0.181269 = 181.27$

The expected refund amount for a dishwasher is $181.27.

## 4b
```{r}
rm(list=ls())
n1 = 10^4
n2 = 10^6

a.exp = 181.27 #expected amount

x1 = rexp(n1, rate=1/10) #exponential rate with mean 10
y1 = ifelse(x1<2,1000,0) #1000 refund if lifespan is under 2 years
est1 = mean(y1)

x2 = rexp(n2, rate=1/10)
y2 = ifelse(x2<2,1000,0)
est2 = mean(y2)

error1 = abs(est1 - a.exp) #difference in calculated mean from true error
error2 = abs(est2 - a.exp)
diff = error1 - error2
```

Mean estimate when $n = 10^4$ is ``r est1``. Mean estimate when $n = 10^6$ is ``r est2``. Compared to the true answer computed analytically, the error for when $n = 10^6$ is ``r diff`` smaller than when $n = 10^4$.

## 4c
```{r}
est.error1 = 1.96*sd(y1)/sqrt(n1) #95% confidence error
CI.low1 = est1 - est.error1
CI.high1 = est1 + est.error1

est.error2 = 1.96*sd(y2)/sqrt(n2)
CI.low2 = est2 - est.error2
CI.high2 = est2 + est.error2
```

When $n = 10^4$, we are 95% confident that the mean refund amount for a dishwasher is between ``r CI.low1`` and ``r CI.high1``. When $n = 10^6$, we are 95% confident that the mean refund amount is between ``r CI.low2`` and ``r CI.high2``.

## 4d
```{r}
n = 1000 #initial sample size
x.initial = rexp(n,rate=1/10)
y.initial = ifelse(x.initial<2, 1000, 0)
hat.sigma = sd(y.initial)
epsilon = 0.5 #error tolerance 50 cents
C = 1.1
N = ceiling((2.58*C*hat.sigma/epsilon)^2) #find new sample size
```

The required simulation size for an error tolerance of 50 cents is ``r N``.

## 5
I struggled initially with 4a to find the correct way to calculate the expected refund amount. However, after I found how to answer 4a, I felt comfortable with the remaining questions since we went over exactly how to do them in the lecture.