---
title: "HW4"
author: "Ian Mulchrone"
date: "2026-01-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 7
a
$$Z = g(X) = (2)1000\frac{1}{10}e^{-X/10}$$
```{r}
rm(list=ls())
n = 1000 #initial sample size
epsilon = 0.50 #error tolerance 50 cents
C= 1.1

#New simulation size with more efficient estimator
x = runif(n,0,2)
y = 2*1000*1/10*exp(-x/10)
sigma.hat = sd(y)
N = ceiling((2.58*C*sigma.hat/epsilon)^2)
```
The simulation size with an error tolerance of 50 cents is ``r N``.


b
```{r}
#Previous simulation size from 4d
x.prev = rexp(n,rate=1/10)
y.prev = ifelse(x.prev<2, 1000, 0)
sigma.prev = sd(y.prev)
N.prev = ceiling((2.58*C*sigma.prev/epsilon)^2)
comp.size = round(N.prev/N)
```

The simulation size of the previous estimator was ``r N.prev`` which is about ``r comp.size`` times larger than the more efficient estimator.

c
```{r}
X = runif(N,0,2) #new sample size
Y = 2*1000*1/10*exp(-X/10) #new simulated sample of refunds
CI.high = mean(Y) + 1.96*sd(Y)/sqrt(N) #95% confidence interval bounds
CI.low = mean(Y) - 1.96*sd(Y)/sqrt(N)
a.true = 181.27 #expected amount
```

We are 95% confident the expected refund to be between ``r CI.low`` and ``r CI.high`` which contains the true answer ``r a.true``.

## 8

a
```{r}
S.0 = 100
r = 0.03
vol = 0.3
MT = 1

#Strike price $75
K = 75
exact.call.price75 = S.0*pnorm((log(S.0/K)+(r+vol^2/2)*MT)/(vol*sqrt(MT)))-K*exp(-r*MT)*pnorm((log(S.0/K)+(r-vol^2/2)*MT)/(vol*sqrt(MT)))

#Strike price $100
K = 100
exact.call.price100 = S.0*pnorm((log(S.0/K)+(r+vol^2/2)*MT)/(vol*sqrt(MT)))-K*exp(-r*MT)*pnorm((log(S.0/K)+(r-vol^2/2)*MT)/(vol*sqrt(MT)))

#Strike price $130
K = 130
exact.call.price130 = S.0*pnorm((log(S.0/K)+(r+vol^2/2)*MT)/(vol*sqrt(MT)))-K*exp(-r*MT)*pnorm((log(S.0/K)+(r-vol^2/2)*MT)/(vol*sqrt(MT)))
```

For a strike price of $75, the exact fair option call price is ``r exact.call.price75``.

For a strike price of $100, the exact fair option call price is ``r exact.call.price100``.

For a strike price of $130, the exact fair option call price is ``r exact.call.price130``.

b
```{r}
n = 10^5
x = rnorm(n)
BM = sqrt(MT)*x #sample BM at T
S.T = S.0*exp((r-vol^2/2)*MT+vol*BM) #sample S(T)

#Estimated call price for strike prices $75, $100, and $130
K = 75
disc.call.payoff75 = pmax(S.T-K,0)*exp(-r*MT)
est.call.price75 = mean(disc.call.payoff75)
err75 = abs(est.call.price75-exact.call.price75)

K = 100
disc.call.payoff100 = pmax(S.T-K,0)*exp(-r*MT)
est.call.price100 = mean(disc.call.payoff100)
err100 = abs(est.call.price100-exact.call.price100)

K = 130
disc.call.payoff130 = pmax(S.T-K,0)*exp(-r*MT)
est.call.price130 = mean(disc.call.payoff130)
err130 = abs(est.call.price130-exact.call.price130)

err.highest = pmax(err75,err100,err130) #find largest error
if (err.highest == err75){ #assign highest error label for conclusion
  label='$75'
} else if (err.highest == err100) {
    label='$100'
    } else {label='$130'}
```

The approximate values for the European call option value at strike price \$75 is ``r est.call.price75`` with an error of ``r err75``.

For strike price \$100 the call option value is ``r est.call.price100`` with an error of ``r err100``. 

For strike price \$130 the call option value is ``r est.call.price130`` with an error of ``r err130``.

The strike price that has the largest error is ``r label`` with an error of ``r err.highest``.

c
```{r}
n = 1000 #initial sample size
epsilon = 0.30 #error tolerance 50 cents
C = 1.1
K = 100
r = 0.03
vol = 0.3
MT = 1
x = rnorm(n)
BM = sqrt(MT)*x #sample BM at T
S.T = S.0*exp((r-vol^2/2)*MT+vol*BM) #sample S(T)

disc.call.payoff100 = pmax(S.T-K,0)*exp(-r*MT)
sigma.hat = sd(disc.call.payoff100)
N = ceiling((2.58*C*sigma.hat/epsilon)^2) #find new sample size
```

For the strike price $100, the simulation sample size required for an error tolerance of 30 cents is ``r N``.
