---
title: "In-ClassLab1Shell"
author: "Ian Mulchrone"
output: html_document
---

```{r echo=FALSE,message=FALSE,warning=TRUE,result='asis'}
##load packages
library(knitr)
###settings for R chunks
knitr::opts_chunk$set(echo=TRUE,
               message=FALSE,
               warning=TRUE,
               results='asis') #echo: whether prints the R code; message: whether shows the message outputs; warning: whether shows the warning messages; results: whether contain ## in front of the R output
```

## (b) Delete all existing variables first.

```{r}
rm(list=ls())
```

## (c) Create an nxd matrix to record the numbers of d people for n games 

```{r}
d = 5 #number of people
n = 10^4 #number of games
game.numbers = matrix(NA,nrow=n,ncol=d)
```

## (d) Assign the leftmost person with a random number on [0,1].

```{r}
game.numbers[,1] = runif(n)
```

## (e) Assign numbers to the rest of people in n games.

```{r}
for (i in 2:d){
  game.numbers[,i] = 1/2*(game.numbers[,i-1]+runif(n))
}
```

## (f) Record the winning (1) or losing (0) of each row (game).

```{r}
game.results = c()
for (i in 1:n){
  game.results[i] = any(game.numbers[i,]>0.6)
}
```

## (g) Count the number of times that we win.

```{r}
number.wins = sum(game.results)
```

## (h) Compute the estimated probability.

```{r}
est.prob = number.wins/n
```

## (i) Compute the confidence interval.

```{r}
CI.low = est.prob - 2.58*sqrt(est.prob*(1-est.prob)/n)
CI.high = est.prob + 2.58*sqrt(est.prob*(1-est.prob)/n)
```

We are 99% confident that the probability of winning the game falls between ``r CI.low`` and ``r CI.high``
.
