---
title: "In-ClassLab6"
author: "Ian Mulchrone"
output: html_document
---

```{r echo=FALSE,message=FALSE,warning=FALSE}
library(knitr)
###settings for R chunks
opts_chunk$set(echo=TRUE,
               message=FALSE,
               warning=FALSE,
               results='asis') #echo: whether prints the R code; message: whether shows the message outputs; warning: whether shows the warning messages; results: whether contain ## in front of the R output; fig.keep: show all figures or just the last one in an R chunk
```

### 1. Run many simulations (say 10000) where you randomly select one of the three doors. After the first door is opened, the selected door is then switched to the other remaining door. We can then calculate the estimated probability of winning based on the number of successes in the 10000 simulations.

### 2. The probability of winning is E(Y).

### 3. 

Define the simulation size.

```{r}
rm(list=ls())
n = 10^4
```

Our goal is to generate a sample of game results. Thus, create vectors to store the sampled door numbers and game results.

```{r}
car.door = c() #the door numbers with the car
player.door = c() #the door numbers the player chooses
host.open = c() #the door numbers the host opens
player.final = c() #the door numbers the player finally switches to
game.result=c()
```


For each one of the $n$ games, we need to repeat the steps described in the in-class lab 6 document. The simplest way to do this is to use a "for loop". We use "i" to denote the numbering of the game. 

```{r}
for (i in 1:n){
  ### randomly pick a door for the car
  car.door[i] = sample(1:3,1)
  ### the player randomly pick a door
  player.door[i] = sample(1:3,1)
  ### the host opens a door with a goat. There are two scenarios.
    if (car.door[i] == player.door[i]){
      available.doors = setdiff(1:3,car.door[i])
      host.open[i] = sample(available.doors,1)
    } else{
      host.open[i] = setdiff(1:3,c(car.door[i],player.door[i]))
    }
  ### player switches the door
  player.final[i] = setdiff(1:3,c(host.open[i],player.door[i]))
  ### the result of the ith game
  game.result[i] = ifelse(player.final[i]==car.door[i],1,0)
}
```

### 4. 99% confidence interval of true probability/proportion is
$$\hat{p}\pm 2.58\sqrt{\frac{\hat{p}(1-\hat{p})}{n}}.$$

```{r}
est.prob = mean(game.result)
est.error = 2.58*sqrt((est.prob*(1-est.prob))/n)
CI.low = est.prob - est.error
CI.high = est.prob + est.error
```
With a simulation size of ``r n``, we are 99% confident that the probability of winning if the player switches the door is between ``r CI.low`` and ``r CI.high``.


### 5. Based on the 99% confidence interval, I believe Vos Savant is correct because the probability of winning when switching the doors is about 2/3 of the time. If you don't switch the door, the probability of winning is only 1/3 based on the initial selection of the door.