---
title: "In-ClassLab2"
author: "Ian Mulchrone"
output: html_document
---

```{r echo=FALSE,message=FALSE,warning=FALSE}
library(knitr)
###settings for R chunks
opts_chunk$set(echo=TRUE,
               message=FALSE,
               warning=FALSE,
               results='asis') #echo: whether prints the R code; message: whether shows the message outputs; warning: whether shows the warning messages; results: whether contain ## in front of the R output; fig.keep: show all figures or just the last one in an R chunk
```

## 1. 
### (a) The target random variable Y is the expected payout for the policy.

### (b) The basic random variable X is the survival time of the insured, X~exp(25).

### (c) Y = 50,000 if X<=20; Y=0 if X>20.

### (d) Fair premium = E(Y)

## 2. To estimate the fair premium, which is E(Y), we generate a simple random smaple of Y and use the sample mean of the random sample to estimate E(Y).

## 3.
### (a) 
```{r}
n = 10^3
x = rexp(n,rate=1/25)
```

### (b)
```{r}
y = ifelse(x > 20, 0, 50000)
```

### (c)
```{r}
est.premium = mean(y)
```

### (d)
```{r}
est.error = 2.58*(sd(y)/sqrt(n))
```

### (e) We are 99% confident that the fair premium falls between ``r est.premium - est.error`` and ``r est.premium + est.error``.

## 4. 
```{r}
n = 1000
x.initial = rexp(n,rate=1/25)
y.initial = ifelse(x.initial > 20, 0, 50000)
hat.sigma = sd(y.initial)
epsilon = 5
C = 1.1
N = ceiling((2.58*C*hat.sigma/epsilon)^2)
```
The required sample size is ``r N``.

## 5.
```{r}
x = rexp(N,rate=1/25)
y = ifelse(x > 20, 0, 50000)
est.premium = mean(y)
est.error = 2.58*sd(y)/sqrt(N)
```
The required simulation size is ``r N``. We are 99% confident that the mean of Y falls between ``r est.premium-est.error`` and ``r est.premium+est.error``.


