---
title: "In-ClassLab5"
author: "Ian Mulchrone"
output: html_document
---

```{r echo=FALSE,message=FALSE,warning=FALSE}
library(knitr)
###settings for R chunks
opts_chunk$set(echo=TRUE,
               message=FALSE,
               warning=FALSE,
               results='asis') #echo: whether prints the R code; message: whether shows the message outputs; warning: whether shows the warning messages; results: whether contain ## in front of the R output; fig.keep: show all figures or just the last one in an R chunk
```


## (a).

### i. The inverse funtion of F(x) is
$$F^{-1}(u) = -ln(1/u - 1)$$

### ii. Generate a sample of uniform random numbers

```{r}
rm(list=ls()) #delete all variables
n=10^3 #simulation size
U = runif(n)
```

### iii. Generate a sample of X~F(x) using the inverse distribution transformation.

```{r}
X = -log(1/U-1)
```

### iv. Generate a sample of Y = X^3.

```{r}
Y = X^3
```

## (b) Estimate the mean, E(Y), using the sample mean of Y.

```{r}
est.mu = mean(Y)
```

## (c) Construct a 99% confidence interval for E(Y).

```{r}
est.error = 2.58*sd(Y)/sqrt(n)
CI.low = est.mu - est.error
CI.high = est.mu + est.error
```

We are 99% confident that mean falls between ``r CI.low`` and ``r CI.high``.

## (d) [Insert your conclusion.]
```{r}
true.answer = 0
if (CI.low<=true.answer& CI.high>=true.answer){cat("The confidence interval contains the true answer.")}else{cat("The confidence interval doesn't contain the true answer.")}
```


## (e) Compute the true absolute error of the estimate.

```{r}
true.answer = 0
true.error = abs(true.answer - est.mu)
```

## (f) 

The estimation error for a 99% confidence estimate tends to be much larger than the true error. In this example, the estimation error is ``r est.error``, while the true error is ``r true.error``.