---
title: "In-Class Lab 8 Shell"
author: "Ian Mulchrone"
output: html_document
---


```{r echo=FALSE,message=FALSE,warning=FALSE}
library(knitr)
###settings for R chunks
opts_chunk$set(echo=TRUE,
               message=FALSE,
               warning=FALSE,
               results='asis') #echo: whether prints the R code; message: whether shows the message outputs; warning: whether shows the warning messages; results: whether contain ## in front of the R output; fig.keep: show all figures or just the last one in an R chunk
```

### 1. $$\mu = E[\frac{3}{4}e^{-x^2}]$$, where X~U[0,0.75]

### 2. Simple Monte Carlo estimator

```{r}
rm(list=ls())
n = 1000
x = runif(n,0,0.75)
y = 3/4*exp(-x^2)
est.smc = mean(y)
error.smc = 2.58*sd(y)/sqrt(n)
CI.low = est.smc - error.smc
CI.high = est.smc + error.smc
```
We are 99% confident the integral is between ``r CI.low`` and ``r CI.high``.

### 3. Use X~U[0, 0.75] as control variate

```{r}
mu.x = 0+0.75/2
beta.hat = cov(x,y)/var(x)
W = y+beta.hat*(mu.x-x)
est.CVX = mean(W)
error.CVX = 2.58*sd(W)/sqrt(n)
CI.low = est.CVX - error.CVX
CI.high = est.CVX + error.CVX
```
Using the control variate X, we are 99% confident the integral is between ``r CI.low`` and ``r CI.high``.

### 4. Use Z = e^(-X) as the control variate

```{r}
z = exp(-x)
mu.z = (1-exp(-0.75))/0.75
beta.hat = cov(z,y)/var(z)
W = y+beta.hat*(mu.z-z)
est.CVZ = mean(W)
error.CVZ = 2.58*sd(W)/sqrt(n)
CI.low = est.CVZ - error.CVZ
CI.high = est.CVZ + error.CVZ
```
Using the control variate Z, we are 99% confident the integral is between ``r CI.low`` and ``r CI.high``.

### 5. Both the control variate estimators will produce a more narrow confidence interval than the simple Monte Carlo estimator because X and Z are both correlated with Y. The control variate X has the smaller confidence error than Z, so the control variate X estimator is the most efficient.

### 6. Compute the correlation between the target random variable and control variate

```{r}
cor.x = cor(x,y)
cor.z = cor(z,y)
```
The correlation between X and Y is ``r cor.x`` and the for Z and Y it is ``r cor.z``. Since the correlation for X and Y is larger, that makes the estimator more accurate, creating a smaller confidence interval.

### 7. Compare to the true answer.

```{r}
true.answer = sqrt(pi)*(pnorm(0.75*sqrt(2))-0.5)
true.error.SMC = abs(est.smc - true.answer)
true.error.CVX = abs(est.CVX - true.answer)
true.error.CVZ = abs(est.CVZ - true.answer)
```

The true answer for Y is ``r true.answer``.
The true error for the SMC is ``r true.error.SMC``.
The true error for the control variate X is ``r true.error.CVX``.
The true error for the control variate Z is ``r true.error.CVZ``.
This conclusion agrees with our answer in #5 since the true error for control variate X is the smallest.