---
title: "In-ClassLab3"
author: "Put Your Name"
output: html_document
---

```{r echo=FALSE,message=FALSE,warning=FALSE}
library(knitr)
###settings for R chunks
opts_chunk$set(echo=TRUE,
               message=FALSE,
               warning=FALSE,
               results='asis') #echo: whether prints the R code; message: whether shows the message outputs; warning: whether shows the warning messages; results: whether contain ## in front of the R output; fig.keep: show all figures or just the last one in an R chunk
```

## 1. 

In the new Monte Carlo estimator, we choose the basic random variable, Z, to follow a uniform distribution on [0,20]. And, the target random variable, W = 50000(20)/25*exp(-Z/25). The goal is to estimate the population mean of W, denoted as E(W). 

### (b) 

Define the sample size

```{r}
n = 10^3
```


To generate a sample of W, we generate a sample of Z~U[0,20].

```{r}
z = runif(n,min=0,max=20) #a sample from U[0,20] 
```

Using the sample of Z, we generate the sample of W = 50000(20)/25*exp(-Z/25).

```{r}
w = 50000*20/25*exp(-z/25)
```

We construct a 99% confidence interval for the mean of W, E(W). The formula is
$$\bar{W}\pm 2.58\frac{\hat{\sigma}_W}{\sqrt{n}}.$$

```{r}
CI.low= mean(w) - 2.58*sd(w)/sqrt(n)
CI.high= mean(w) + 2.58*sd(w)/sqrt(n)
```

The conclusion is: We are 99% confident that the fair premium will fall between ``r CI.low`` and ``r CI.high``.

### (c)  

If we would like the estimation error to be within an absolute error tolerance of $\varepsilon=5$ dollars, using the sample of W generated above, we can find the required simulation size by formula
$$n = \lceil (2.58C\hat{\sigma}/\varepsilon)^2\rceil.$$

```{r}
sigma_hat = sd(w)
C = 1.1
epsilon = 5
N = ceiling((2.58*C*sigma_hat/epsilon)^2)#required simulation size
```

The required simulation size of the new Monte Carlo estimator is ``r N``. 

### (d)

By using a more efficient sampling method, the required simulation size is significantly smaller. Compared to the previous estimator using a basic random variable, the required simulation size is about 20 times smaller with the target random variable method.

