---
title: "In-ClassLab4"
author: "Ian Mulchrone"
output: html_document
---

```{r echo=FALSE,message=FALSE,warning=FALSE}
library(knitr)
###settings for R chunks
opts_chunk$set(echo=TRUE,
               message=FALSE,
               warning=FALSE,
               results='asis') #echo: whether prints the R code; message: whether shows the message outputs; warning: whether shows the warning messages; results: whether contain ## in front of the R output; fig.keep: show all figures or just the last one in an R chunk
```


We first start with a relatively small simulation size, n=10000, to compute the required simulation size.

Define the variable values.

```{r}
n=10000
K = 45
MT = 0.5
S.0 = 50
r = 0.03
sigma = 0.2
```

To simulate n stock prices at maturity, generate n standard normal random numbers, one for each stock price simulation.

```{r}
#n standard normal random numbers to generate n asset prices at maturity
z = rnorm(n)
```

To simulate stock price at maturity, generate n instances of Brownian motion.

```{r}
#n sampled BM at maturity
BM = sqrt(MT)*z
```

Generate n stock prices at maturity.

```{r}
#n asset prices at maturity
S = S.0*exp((r-sigma^2/2)*MT+sigma*BM)
```

Generate n discounted payoffs.

```{r}
#n discounted payoffs
disc_payoffs = pmax(K-S,0)*exp(r*MT)
```

Compute the required simulation size using the formula
$$n = \lceil (2.58C\hat{\sigma}_{payoff}/\varepsilon)^2\rceil,$$
where $\varepsilon$ is the sample standard deviation of the discounted payoffs we just generated.

```{r}
epsilon = 0.5
C = 1.1
N = 10000
sigma.hat = sd(disc_payoffs)
N = ceiling((2.58*C*sigma.hat/epsilon)^2)
```

Now, we will use the appropriate simulation size to estimate the put option price. For n simulated stock prices at maturity, generate n standard normal random number.

```{r}
z = rnorm(N)
```

To simulate n stock prices at maturity, generate n instances of Brownian motion.

```{r}
BM = sqrt(MT)*z
```

Generate n stock prices at maturity.

```{r}
S.T = S.0*exp((r-sigma^2/2)*MT+sigma*BM)
```

Generate n discounted payoffs.

```{r}
disc.payoffs = pmax(K-S.T,0)*exp(-r*MT)
```

Estimate the fair price of the option using the sample mean of the simulated discounted payoffs.

```{r}
est.put.price = mean(disc.payoffs)
```

Since the underlying asset price is assumed to follow a GBM, the true option price can be computed using Black-Scholes formula.

```{r}
###uncomment the following line when you get here.
ExactEuroPut<-K*exp(-r*MT)*pnorm((log(K/S.0)-(r-sigma^2/2)*MT)/(sigma*sqrt(MT)))-S.0*pnorm((log(K/S.0)-(r+sigma^2/2)*MT)/(sigma*sqrt(MT)))

```

Using the true option price, we can compute the true error.

```{r}
true.price.error = abs(ExactEuroPut - est.put.price)
```

The true error between the Monte Carlo and the exact price is ``r true.price.error`` which is smaller than the pre-set error tolerance of 50 cents.


