---
title: "Untitled"
output: html_document
date: "2026-02-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part 1 (d=12)

n sample paths for jackpot model
```{r}
library(tictoc)
tic()
rm(list = ls())
graphics.off()

S.0=50
K=50
MT=1
r.0=0.07
sigma=0.13

d=12
delta=MT/d
n=10^4

# generate n sample paths
r=matrix(NA,nrow=n,ncol=d+1)
r[,1]=r.0
Z = matrix(rnorm(n*d),nrow=n)
for (j in 2:(d+1)){
  r[,j]=r[,j-1]+0.18*(0.086-r[,j-1])*delta+0.02*sqrt(delta)*Z[,j-1]
}

log.S=matrix(NA,nrow=n,ncol=d+1)
log.S[,1]=log(S.0)
X=matrix(rnorm(n*d),nrow=n)
shape = delta/0.15
scale = 0.15
Y = matrix(rgamma(n*d, shape, scale),nrow=n)

for (j in 2:(d+1)){
  log.S[,j] = log.S[,j-1]+(r[,j-1]+(log(1-0.15*sigma^2/2)/0.15))*delta+sigma*sqrt(Y[,j-1])*X[,j-1]

}
S=exp(log.S)
S.MT = S[,d+1]

call.payoff= pmax(S.MT-K,0)
disc.factor = exp(-delta*rowSums(r[,2:(d+1)]))
call.discpayoff = call.payoff*disc.factor
est.price = mean(call.discpayoff)

est.error = sd(call.discpayoff)/sqrt(n)
ci.low = est.price - 2.58 * est.error
ci.high = est.price + 2.58 * est.error


toc()

```


```{r}
# Find required simulation size
epsilon = 0.05
C=1.1
N = ceiling((2.58*C*sd(call.discpayoff)/epsilon)^2)
```
The appropriate sample size should be ``r N`` to assure the estimation error is no larger than 5 cents.


Rerun model with n=N
```{r}
tic()
# generate N sample paths
n = N #using required simulation size

r=matrix(NA,nrow=n,ncol=d+1)
r[,1]=r.0
Z = matrix(rnorm(n*d),nrow=n)
for (j in 2:(d+1)){
  r[,j]=r[,j-1]+0.18*(0.086-r[,j-1])*delta+0.02*sqrt(delta)*Z[,j-1]
}

log.S=matrix(NA,nrow=n,ncol=d+1)
log.S[,1]=log(S.0)
X=matrix(rnorm(n*d),nrow=n)
shape = delta/0.15
scale = 0.15
Y = matrix(rgamma(n*d, shape, scale),nrow=n)

for (j in 2:(d+1)){
  log.S[,j] = log.S[,j-1]+(r[,j-1]+(log(1-0.15*sigma^2/2)/0.15))*delta+sigma*sqrt(Y[,j-1])*X[,j-1]

}
S=exp(log.S)
S.MT = S[,d+1]

call.payoff= pmax(S.MT-K,0)
disc.factor = exp(-delta*rowSums(r[,2:(d+1)]))
call.discpayoff = call.payoff*disc.factor
est.price = mean(call.discpayoff)

est.error = sd(call.discpayoff)/sqrt(n)
ci.low.a = est.price - 2.58 * est.error
ci.high.a = est.price + 2.58 * est.error

toc()
```
est.price = ``r est.price``
est.error = ``r est.error``
ci.low = ``r ci.low.a``
ci.high = ``r ci.high.a``


## Part 2 (d=52)

```{r}
tic()

d=52
n=1000
delta=MT/d

# generate n sample paths
r=matrix(NA,nrow=n,ncol=d+1)
r[,1]=r.0
Z = matrix(rnorm(n*d),nrow=n)
for (j in 2:(d+1)){
  r[,j]=r[,j-1]+0.18*(0.086-r[,j-1])*delta+0.02*sqrt(delta)*Z[,j-1]
}

log.S=matrix(NA,nrow=n,ncol=d+1)
log.S[,1]=log(S.0)
X=matrix(rnorm(n*d),nrow=n)
shape = delta/0.15
scale = 0.15
Y = matrix(rgamma(n*d, shape, scale),nrow=n)

for (j in 2:(d+1)){
  log.S[,j] = log.S[,j-1]+(r[,j-1]+(log(1-0.15*sigma^2/2)/0.15))*delta+sigma*sqrt(Y[,j-1])*X[,j-1]

}
S=exp(log.S)
S.MT = S[,d+1]

call.payoff= pmax(S.MT-K,0)
disc.factor = exp(-delta*rowSums(r[,2:(d+1)]))
call.discpayoff = call.payoff*disc.factor
est.price = mean(call.discpayoff)

est.error = sd(call.discpayoff)/sqrt(n)
ci.low = est.price - 2.58 * est.error
ci.high = est.price + 2.58 * est.error
toc()
```


Find required sample size
```{r}
epsilon = 0.05
C=1.1
N = ceiling((2.58*C*sd(call.discpayoff)/epsilon)^2)
```
The appropriate sample size should be ``r N`` to assure the estimation error is no larger than 5 cents.


N sample paths
```{r}
tic()
# generate N sample paths
n = N #using required simulation size

r=matrix(NA,nrow=n,ncol=d+1)
r[,1]=r.0
Z = matrix(rnorm(n*d),nrow=n)
for (j in 2:(d+1)){
  r[,j]=r[,j-1]+0.18*(0.086-r[,j-1])*delta+0.02*sqrt(delta)*Z[,j-1]
}

log.S=matrix(NA,nrow=n,ncol=d+1)
log.S[,1]=log(S.0)
X=matrix(rnorm(n*d),nrow=n)
shape = delta/0.15
scale = 0.15
Y = matrix(rgamma(n*d, shape, scale),nrow=n)

for (j in 2:(d+1)){
  log.S[,j] = log.S[,j-1]+(r[,j-1]+(log(1-0.15*sigma^2/2)/0.15))*delta+sigma*sqrt(Y[,j-1])*X[,j-1]

}
S=exp(log.S)
S.MT = S[,d+1]

call.payoff= pmax(S.MT-K,0)
disc.factor = exp(-delta*rowSums(r[,2:(d+1)]))
call.discpayoff = call.payoff*disc.factor
est.price = mean(call.discpayoff)

est.error = sd(call.discpayoff)/sqrt(n)
ci.low.b = est.price. - 2.58 * est.error
ci.high.b = est.price. + 2.58 * est.error
toc()
```

est.price = ``r est.price``
est.error = ``r est.error``
ci.low = ``r ci.low.b``
ci.high = ``r ci.high.b``



